Mimicry in Online Conversations: An Exploratory Study of Linguistic Analysis Techniques

### 2016-04-23 papers/asonam2016/paper.tex
Progress

[Maybe should mention here that LILLA and SILLA do mention lexical/syntactic levels explicitly which
is probably the exception. Everything else either naturally fits into a layer (HAM), haven't really
been used for mimicry before as far as I know (word/paragraph vectors), or aren't specifically
targeted at a layer (LSM, Zelig). Not sure if I want to mention all this in the introduction though.]

This perspective is important so that each measure is grounded [too much grounded] in reality.
Moreover, it suggests [does it?] that the best approach may be to combine existing measures to create
a more holistic measure. [don't like any of this wording].

[I feel like I want a "this study aims to x y and z" here]

\section{Background}

[if we only want to discuss IAM here should we retitle this section?]

The Interactive Alignment Model (IAM)\cite{pickering2004toward} is an attempt to model alignment in
conversations. It consists of six layers, which with the exception of the top layer, the situation model,
are all representations of some aspect of speech.

@@

[Do we really need both list and figure?]

The phonological and phonetic layers are ignored by this paper as they do not relate to written text.
[should I just leave them out of the list?]

@@

[Figure takes up over half a page. Might be an idea to use a different one, or cut off phon* layers.
Not sure if I can go around stealing people's images either.]

\section{Method}
I'm not exactly sure what experiments we will have yet,
or if we need to name this section something else entirely.

Do we maybe have a subsection for each layer and a subsubsection for each measure?
We should explain somewhere why we skip situation, phonological and phonetic layers.

@@

\subsubsection{LILLA}
LILLA\cite{wang2014linguistic, xu2015evaluation}

\subsubsection{HAM}
HAM\cite{doyle2016robust}

@@

\subsubsection{SILLA}
SILLA

@@

\subsubsection{doc2vec}
doc2vec\cite{le2014distributed}. Consider also sense2vec\cite{trask2015sense2vec} and/or doc2vec sense2vec hybrid?

@@

\section{Results}
Same here, not sure what results we will have.

@@

% use section* for acknowledgment
\section*{Acknowledgment}
Do we need to thank CREST for giving us money here?

>>>>

This perspective is important so that each measure is grounded in reality.
Moreover, it suggests [does it?] that the best approach may be to combine existing measures to create
a more holistic measure. [don't like any of this wording].

Of the measures discussed in this paper, only one has attempted to measure alignment with this in mind
and some, such as LSM seem to work outside of the theory altogether.

This paper aims to compare how well existing linguistic analysis techniques work to detect mimicry in 
relation to the Interactive Alignment Model. Further, we also look at some existing techniques that 
have not previously been used to detect mimicry and discuss their viability.

[Not sure what else to put here. Section II does this, section III looks at that type thing?]

\section{Related Work}
This paper draws from many sources for its measures. The most similar piece of work is a comparison
of several methods\cite{xu2015evaluation}, some discussed in this paper. It does not, however, try
to compare the accuracy of the measures, rather, it [does some stuff I don't understand that well,
seems like it looks at some statistical properties?]

[Not sure what else to mention here]

\section{The Interactive Alignment Model}
The Interactive Alignment Model (IAM)\cite{pickering2004toward} is an attempt to model alignment in
conversations. It consists of six layers, which with the exception of the top layer, the situation
model, are all representations of some aspect of speech.

@@

The phonological and phonetic layers are ignored by this paper as they do not relate to written text.

@@

\section{Method}

\subsection{Data}
The dataset consists of 103 dyadic conversations taken from Twitter. Tweets were found via Twitter's 
search API, using English language and being a reply as criteria. We then work up the chain of tweets 
until we hit the end, or a third interlocutor is found, at which point the conversation is cut off and 
kept, as long as there are no fewer than 10 tweets in the conversation. 200 tweets were found using 
this method. Of these, 62 were removed as they were not true conversations (either monologues or 
collaborative fiction writing/roleplay). 18 conversations were removed as they had significant amounts 
of non-English text, and 17 conversations involved bots and were also removed.

The data is processed as follows:
\begin{itemize}
	\item Screen names at the start of the message are removed. These are just the names of the 
		  interlocutors and only add noise.
	\item All URLs are replace with the string '[URL]'.
	\item HTML entities such as \&amp; are converted to plain text (\&).
	\item Any adjacent messages by the same author are merged together such that each message always
	      alternates between the two interlocutors.
\end{itemize}

The data was classified by three PhD students at Lancaster University with backgrounds in mimicry. Each 
conversation was classified for lexical, syntactic and semantic mimicry on a three point scale where 0 
represents no mimicry, 1 represents low levels of mimicry at that layer, and 2 represents high levels 
of mimicry.

Each measure, with exceptions noted in following subsections [Probably just HAM at this point],
is then run against the data such that each message from author A is compared with each message from 
author B that occurred before the original message.
\footnote{[I could probably make my github repo public and put a link to the code here?]}

[Need to justify dataset and discuss limitations]

@@

\subsubsection{LILLA}
Lexical Indiscriminate Local Linguistic Alignment (LILLA)\cite{wang2014linguistic, xu2015evaluation}
is a measure that explicitly works at the lexical layer. It gives the probability that a word from the 
prime document will appear at a particular position in the target document. It is defined as:

\[LILLA(target, prime) = \frac{p(target|prime)}{p(target)}\]

\subsubsection{HAM}
The Hierarchical Alignment Model (HAM)\cite{doyle2016robust} ...

@@

\subsubsection{SILLA}
Syntactic Indiscriminate Local Linguistic Alignment (SILLA)

@@

\subsubsection{doc2vec}
doc2vec\cite{le2014distributed}.

@@

\section{Results}
Still not sure how to compare everything.

@@

% use section* for acknowledgment
\section*{Acknowledgment}
The authors gratefully acknowledge a grant from CREST (probably need to find the name of this).
